---
title: "Nana  Boateng's Resume"
author: Nana Boateng
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
  
    css: ['css/resume_styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- TRUE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

# Load csv with position info
position_data <- read_csv('resume_positions.csv')

```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-envelope"></i> unltd148@yahoo.co.uk
- <i class="fa fa-link"></i> [restanalytics.com/](http://restanalytics.com/)
- <i class="fa fa-github"></i>[github](https://github.com/NanaAkwasiAbayieBoateng)
- <i class="fa fa-phone"></i> (901) 246-7618
- <i class="fa fa-linkedin"></i> [linkedin](https://www.linkedin.com/in/nana-boateng-26b9a226/)



Skills {#skills}
--------------------------------------------------------------------------------

- <i class="fa fa-laptop"></i> **Programming**: Python, R,SQL, Scala, Spark,
Matlab, SAS,Octave
- <i class="fa fa-flask"></i> **Cloud Computing**: AWS sagemaker, 
Microsoft Azure, Google cloud, Databricks,
- <i class="fa fa-lightbulb-o"></i> **Other**: Tensorflow/Keras, pyTorch,Scikit-learn,tidyverse, plotly, matplotlib, ggplot2,Stata, Minitab, 
Tableau, Power BI, Github/Bitbucket, SPSS, Linux/Unix, Docker


Credentials
--------------------------------------------------------------------------------

- <i class="fa fa-chart-area"></i> SQL and Relational Databases – IBM ,2021
- <i class="fa fa-drivers-license"></i> Professional Educator License (IL): Docker Essentials – A developer Introduction, IBM, 2020
- <i class="fa fa-drivers-license"></i> Data Science with Scala - IBM, 2020
- <i class="fa fa-drivers-license"></i> Certified Base Programmer – SAS


<!-- Disclaimer {#disclaimer} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).  -->

<!-- The source code is available at [github.com/NanaAkwasiAbayieBoateng/cv](https://github.com/NanaAkwasiAbayieBoateng/cv). -->


<!-- Last updated on `r Sys.Date()`. -->


Main
================================================================================

Nana Boateng {#title}
--------------------------------------------------------------------------------
Nana Boateng is a Data Scientist with professional experience in machine learning, Deep learning, computer vision, natural language processing, optimization techniques, predictive analytics, statistical analysis and spatial data visualization.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```


Professional Experience {data-icon=key}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'professional_positions')
```




<!-- :::aside -->

<!-- Peer-reviewed Publications -->
<!-- -------------------------------------------------------------------------------- -->
<!-- - [Splicing modulation sensitizes chronic lymphocytic leukemia cells to venetoclax by remodeling mitochondrial apoptotic dependencies](https://www.ncbi.nlm.nih.gov/pubmed/30282833). Ten Hacken E et al. (2018), JCI Insight 3(19). -->
<!-- - [Identification of Novel Protein Expression Changes Following Cisplatin Treatment and Application to Combination Therapy](https://www.ncbi.nlm.nih.gov/pubmed/28902521). Stark AL et al (2017). Journal of Proteome Research, 16(11): 4227-4236. -->
<!-- - [Truncated DNMT3B isoform DNMT3B7 suppresses growth, induces differentiation, and alters DNA methylation in human neuroblastoma.](https://www.ncbi.nlm.nih.gov/pubmed/22815530). Ostler KR et al (2012). Cancer Research 72(18): 4714-23. -->


<!-- Posters and Presentations -->
<!-- -------------------------------------------------------------------------------- -->
<!-- - [The role of PRDM1 in protection against radiogenic breast cancer.](https://github.com/gillsignals/science-docs/blob/master/prdm1_talk_140305.pptx) Oral presentation, Dept. Pediatric Hem/Onc, UChicago (2014). -->
<!-- - The role of Blimp1 in protection against ionizing radiation in breast cells. Poster, Biomedical Sciences Retreat, UChicago (2014). -->
<!-- - Systems analysis of cytarabine response and resistance in hematopoietic cells. Poster, Biomedical Sciences Retreat, UChicago (2013). -->
<!-- ::: -->

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'teaching_positions')
```



Peer-reviewed Publications {data-icon=flask}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'publications')
```



```{r eval=FALSE}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


